Contracts for Contracts

### 2023-07-09 paper/case_study.tex
add evaluation plan
background section [WIP]
add attack list

\section{Case Studies} \label{sec:case}

@@

\subsection{Reentrancy}

@@

>>>>

\section{Case Studies} \label{sec:case}
\begin{itemize}
	\item Overall result in preventing several real-world attacks.
\end{itemize}

@@

\subsection{Reentrancy}
Market.xyz readonly reentrancy attack.
Transfer return value not checked.
Li.fi attack: Arbitrary call to untrusted code (low-level call).

@@

\begin{table}
	\centering
	\begin{tabular}{cccc}
		\toprule
		\textbf{Type} & \textbf{Case} & \textbf{Date} & \textbf{Loss} \\
		\midrule
		\multirow{4}{*}{\rotatebox[origin=c]{90}{\begin{tabular}{@{}c@{}}Readonly \\Reentrancy\end{tabular}}} 
		& \href{https://medium.com/coinmonks/theoretical-practical-balancer-and-read-only-reentrancy-part-1-d6a21792066c}{Sentiment} & 04/05/23 & \$1M \\
		& \href{https://twitter.com/BlockSecTeam/status/1623901011680333824
		}{dForce} & 02/10/23 & \$3.65M \\
		& \href{https://twitter.com/peckshield/status/1614774855999844352}{MidasCapital} & 01/16/23 & \$650K \\ 
		& \href{https://quillaudits.medium.com/decoding-220k-read-only-reentrancy-exploit-quillaudits-30871d728ad5}{Market.xyz} & 10/24/22 & \$220K \\

		\midrule

		\multirow{10}{*}{\rotatebox[origin=c]{90}{Arbitrary External Call}} 
		& \href{https://twitter.com/hexagate_/status/1671188024607100928?cxt=HHwWgMC--e2poLEuAAAA}{MIMSpell} & 06/20/23 & \$17K \\
		& \href{https://twitter.com/HypernativeLabs/status/1633090456157401088}{Phoenix} & 03/07/23 & \$100K \\
		& \href{https://mirror.xyz/revertfinance.eth/3sdpQ3v9vEKiOjaHXUi3TdEfhleAXXlAEWeODrRHJtU}{RevertFinance} & 02/18/23 & \$30K \\
		& \href{https://twitter.com/peckshield/status/1626493024879673344}{Dexible} & 02/12/23 & \$1.5M \\
		& \href{https://twitter.com/peckshield/status/1622801412727148544}{CowSwap} & 02/07/23 & \$120K \\
		& \href{https://twitter.com/BlockSecTeam/status/1606993118901198849}{Rubic} & 12/25/22 & \$1.5M \\
		& \href{https://twitter.com/SlowMist_Team/status/1590685173477101570}{BrahTOPG} & 11/09/22 & \$89k \\
		& \href{https://twitter.com/Supremacy_CA/status/1590337718755954690}{MEV\_0ad8} & 11/08/22 & \$282k \\
		& \href{https://twitter.com/Supremacy_CA/status/1579813933669486592}{Rabby} & 10/11/22 & \$200K \\
		& \href{https://blog.li.fi/20th-march-the-exploit-e9e1c5c03eb9}{Li.Fi} & 03/20/22 & \$570K \\

		\midrule

		\multirow{5}{*}{\rotatebox[origin=c]{90}{\begin{tabular}{@{}c@{}}Return Value\\Not Check\end{tabular}}} 
		& & & \\
		& & & \\
		& \href{https://medium.com/@QubitFin/protocol-exploit-report-305c34540fa3}{Qubit} & 01/28/22 & \$80M \\
		& & & \\
		& & & \\
		\bottomrule
	\end{tabular}
	\caption{Summary of case studies.}
	\label{tab:case}
\end{table}
